LAGOS lake depth

### 2020-11-24 tables/01_predictors.Rmd
linting

```{r predictors_table}
# setwd("figures")
(slope_distance_vars <- unique(dt_combined$variable)[
  stringr::str_detect(unique(dt_combined$variable), 
                     "dist_|e_slope_|dists_|e_slopes")])
(exclude_vars <- unique(dt_combined$variable)[
  stringr::str_detect(unique(dt_combined$variable), 
                     "totalarea|islandperimeter|between|buffer100m|lake_meandepth_m")])

>>>>

```{r predictors_table}
# setwd("figures")
slope_distance_vars <- unique(dt_combined$variable)[
  stringr::str_detect(unique(dt_combined$variable), 
                     "dist_|e_slope_|dists_|e_slopes")]
exclude_vars <- unique(dt_combined$variable)[
  stringr::str_detect(unique(dt_combined$variable), 
                     "totalarea|islandperimeter|between|buffer100m|lake_meandepth_m")]
